Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-03-17 paper.qmd
Updated with projection function

model_df <- dplyr::left_join(
  distance_df_small_edges_two_curvy |> select(-distance), 
  projected_model_df, 
  by = c("from" = "ID"))

@@

projected_model <- as.matrix(scaled_two_curvy_data_model) %*% projection_scaled

model_df <- dplyr::left_join(
  wireframe_true_model, 
  projected_model_df, 
  by = c("from" = "ID"))

axes_obj <- gen_axes(  
  proj = projection * 2,
  limits = 0.6,
  axis_pos_x = -0.4,
  axis_pos_y = -0.4,
  axis_labels = names(scaled_two_curvy_data),
  threshold = 0.04)

@@

projected_model <- as.matrix(scaled_two_curvy_data_model) %*% projection_scaled

model_df <- dplyr::left_join(
  wireframe_true_model, 
  projected_model_df, 
  by = c("from" = "ID"))

axes_obj <- gen_axes(  
  proj = projection * 6,
  limits = 0.5,
  axis_pos_x = -0.3,
  axis_pos_y = -0.3,
  axis_labels = names(scaled_two_curvy_data),
  threshold = 0)

@@

model_df <- dplyr::left_join(
  distance_df_small_edges_two_curvy2 |> select(-distance), 
  projected_model_df, 
  by = c("from" = "ID"))

@@

axes_obj <- gen_axes(  
  proj = projection * 5,
  limits = 0.15,
  axis_pos_x = -0.067,
  axis_pos_y = -0.067,
  axis_labels = names(scaled_two_curvy_data),
  threshold = 0.007)

>>>>

proj_obj1 <- get_projection(projection = projection, 
               proj_scale = 1, 
               scaled_data = scaled_two_curvy_data, 
               scaled_data_model = scaled_two_curvy_data_model, 
               distance_df_small_edges = distance_df_small_edges_two_curvy, 
               axis_param = list(limits = 0.5, 
                                 axis_scaled = 2,
                                 axis_pos_x = -0.5, 
                                 axis_pos_y = -0.5, 
                                 threshold = 0.03))

@@

proj_obj1 <- get_projection(projection = projection, 
               proj_scale = 1, 
               scaled_data = scaled_two_curvy_data, 
               scaled_data_model = scaled_two_curvy_data_model, 
               distance_df_small_edges = distance_df_small_edges_two_curvy, 
               axis_param = list(limits = 0.6, 
                                 axis_scaled = 2,
                                 axis_pos_x = -0.4, 
                                 axis_pos_y = -0.4, 
                                 threshold = 0.04))

# projection_scaled <- projection * 1
# 
# projected <- as.matrix(scaled_two_curvy_data) %*% projection_scaled
# 
# projected_df <- projected |>
#   tibble::as_tibble(.name_repair = "unique") |>
#   dplyr::rename(c("proj1" = "...1",
#                   "proj2" = "...2")) |>
#   #dplyr::mutate(type = df_exe$type) |>
#   dplyr::mutate(ID = dplyr::row_number()) 
# 
# projected_model <- as.matrix(scaled_two_curvy_data_model) %*% projection_scaled
# 
# projected_model_df <- projected_model |>
#   tibble::as_tibble(.name_repair = "unique") |>
#   dplyr::rename(c("proj1" = "...1",
#                   "proj2" = "...2")) |>
#   dplyr::mutate(ID = dplyr::row_number())
# 
# model_df <- dplyr::left_join(
#   wireframe_true_model, 
#   projected_model_df, 
#   by = c("from" = "ID"))
# 
# names(model_df)[3:NCOL(model_df)] <- paste0(names(projected_model_df)[-NCOL(projected_model_df)], "_from")
# 
# model_df <- dplyr::left_join(model_df, projected_model_df, by = c("to" = "ID"))
# names(model_df)[(2 + NCOL(projected_model_df)):NCOL(model_df)] <- paste0(names(projected_model_df)[-NCOL(projected_model_df)], "_to")
# 
# axes_obj <- gen_axes(  
#   proj = projection * 2,
#   limits = 0.6,
#   axis_pos_x = -0.4,
#   axis_pos_y = -0.4,
#   axis_labels = names(scaled_two_curvy_data),
#   threshold = 0.04)
# 
# axes <- axes_obj$axes
# circle <- axes_obj$circle

@@

proj_obj2 <- get_projection(projection = projection, 
               proj_scale = 1, 
               scaled_data = scaled_two_curvy_data, 
               scaled_data_model = scaled_two_curvy_data_model, 
               distance_df_small_edges = distance_df_small_edges_two_curvy, 
               axis_param = list(limits = 0.5, 
                                 axis_scaled = 6,
                                 axis_pos_x = -0.3, 
                                 axis_pos_y = -0.3, 
                                 threshold = 0))

@@

proj_obj1 <- get_projection(projection = projection, 
                            proj_scale = 1, 
                            scaled_data = scaled_gau_data, 
                            scaled_data_model = scaled_gau_data_model, 
                            distance_df_small_edges = distance_df_small_edges, 
                            axis_param = list(limits = 0.15, 
                                              axis_scaled = 5,
                                              axis_pos_x = -0.067, 
                                              axis_pos_y = -0.067, 
                                              threshold = 0.007))

# projection_scaled <- projection * 1
# 
# projected <- as.matrix(scaled_two_curvy_data) %*% projection_scaled
# 
# projected_df <- projected |>
#   tibble::as_tibble(.name_repair = "unique") |>
#   dplyr::rename(c("proj1" = "...1",
#                   "proj2" = "...2")) |>
#   dplyr::mutate(ID = dplyr::row_number()) 
# 
# ## For fitted model
# projected_model <- as.matrix(scaled_two_curvy_data_model) %*% projection_scaled
# 
# projected_model_df <- projected_model |>
#   tibble::as_tibble(.name_repair = "unique") |>
#   dplyr::rename(c("proj1" = "...1",
#                   "proj2" = "...2")) |>
#   dplyr::mutate(ID = dplyr::row_number())
# 
# model_df <- dplyr::left_join(
#   distance_df_small_edges_two_curvy2 |> select(-distance), 
#   projected_model_df, 
#   by = c("from" = "ID"))
# 
# names(model_df)[3:NCOL(model_df)] <- paste0(names(projected_model_df)[-NCOL(projected_model_df)], "_from")
# 
# model_df <- dplyr::left_join(model_df, projected_model_df, by = c("to" = "ID"))
# names(model_df)[(2 + NCOL(projected_model_df)):NCOL(model_df)] <- paste0(names(projected_model_df)[-NCOL(projected_model_df)], "_to")

@@

# axes_obj <- gen_axes(  
#   proj = projection * 5,
#   limits = 0.15,
#   axis_pos_x = -0.067,
#   axis_pos_y = -0.067,
#   axis_labels = names(scaled_two_curvy_data),
#   threshold = 0.007)
# 
# axes <- axes_obj$axes
# circle <- axes_obj$circle
